Using SMT engine to generate Symbolic Automata\thanks{This work was partially funded by the Associated Team FM4CPS between INRIA and ECNU, Shanghai}

### 2018-01-09 2017-Xudong-SMT/FM-2018-extended.tex
appendix

%% Open pNet framework provides us
%% with a model able to express the semantics of many different algebras
%% or languages. In particular,
As seen in section
\ref{section:pnets}, the \emph{term algebra} used to express the
action expressions and data parameters is left open in
the pNet definition.

@@

\paragraph{Translation of Action algebra presentation}

The $datatypes$ are declared according to the $sorts$ the users
declared in the $presentation$. If the return type of the $functions$
is one of the $datatypes$, we add this $function$ to the $datatypes$ declaration.
So when we declare the operator ACT we illustrated in section 4.1, it
will be just declared together with the constants like :\\
\centerline{$\OTvar{(ACT\ (action3\ Action)(data\ Int))}$}

@@

\paragraph{Translating assignments into predicate terms}

@@

\subsection{Result of the running example}
\label{section:full-result}
% \TODO{
% Xudong: full result of the tool execution on the running example\\\\
% Open Automata of the CCS example.

% \QIN{[The fig is improved. A little change on the comments.]}

% \subsubsection{Result of LOTOS example}

Our tool builds 30 open
transitions, out of which 27 are detected unsatisfiable by Z3, we
get only 3 results left; the resulting open automaton is shown in
Fig. ~\ref{schema:lotos-result}, together with its open transitions.

@@

\begin{figure}[h]
%  \centerline{\includegraphics[width=5cm]{XFIG/LOTOSresult}}

@@

  $\begin{array}{@{}r@{}l@{}}
    ot_3  = &\openrule{\{0 \xrightarrow{r}_{C_1} 0, 1 \xrightarrow{q}_{C_2} 1\}, ~~\{\xrightarrow{hb_{3}}_Q\}, ~~[s_0=1 \!\land\! hb_{3} \neq acc(x) \!\land\! v_3=hb_{3}]}
    {\ostate{01} \xrightarrow{v_3} \ostate{01}}\\
  \end{array}$

@@

@@

% \newpage
% \appendix

>>>>

\TODO{Improve this, inserting the main definition from the ``Checker'' document}
%% Open pNet framework provides us
%% with a model able to express the semantics of many different algebras
%% or languages. In particular,
As seen in section
\ref{section:pnets}, the \emph{term algebra} used to express the
action expressions and data parameters is left open in
the pNet definition.

@@

\paragraph{Translation of Action algebra presentation}
\TODO{Exerpt of the formalisation}
The $datatypes$ are declared according to the $sorts$ the users
declared in the $presentation$. If the return type of the $functions$
is one of the $datatypes$, we add this $function$ to the $datatypes$ declaration.
So when we declare the operator ACT we illustrated in section 4.1, it
will be just declared together with the constants like :\\
\centerline{$\OTvar{(ACT\ (action3\ Action)(data\ Int))}$}

@@

\paragraph{Translating assignments into predicate terms}
\TODO{Exerpt of the formalisation}

@@

\subsection{Result of the running example}
\label{section:full-result}

\TODO{Update: we have 11 satisfiable OTs here}
Our tool builds 30 open
transitions, out of which 27 are detected unsatisfiable by Z3, we
get only 3 results left; the resulting open automaton is shown in
Fig. ~\ref{schema:lotos-result}, together with its open transitions.

@@

\begin{figure}[h]
%  \centerline{\includegraphics[width=5cm]{XFIG/LOTOSresult}}
  \TODO{Detaisl of some OTs of the FailureTimer}

@@

@@

\TODO{Change perspective: we are working on the formal extensino of
  BIB architectures, and their semantics in terms of pNets. Then
  bisimulation and model-checking principles adapted to open pNet
  systems are under development}

@@

% \newpage
\appendix

\section{More details on the generation algorithm}
\subsection{Algebra specification}
\subsection{Term algebra: type system and static semantics}
\subsection{Variable managment}
\subsection{Filtering the behaviour combinations}
\subsection{Translation to SMTlib input language}
\subsection{Elimination of intermediate variables}

\section{Full examples}
\TODO{May be we use two architecture examples here, a simpler one,
  before the Failure Timer ?}
\subsection{A very simple architecture}
\subsection{Full input for the FailureTimer architecture}
\subsection{Full output for the FailureTimer open automaton}
\subsection{Scaling up: several subsystems on the same bus}
